Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-07-19 2016-Weak-FH-Bisim/WeakBisim.tex
qques corrections

\begin{lemma}[Weak OT decomposition]\label{lem-decomposeWOT} 
	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
	lemma imply that $Q$ is 
	not a pLTS but a similar lemma can be proven for a pLTS $Q$}:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.  
		 Then there exist $n$, $\Pred\,'$,  
		$\Post\,'$,   and for all $p\in[0..n]$ there exist $\beta_p$, $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J_p\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
\text{\qquad and \qquad}\gamma_{j_0}=[\beta_0..\beta_n]
	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
		%\[
		Q\models{\openrule
			{
				\gamma_{p j}^{j\in J_p}, \Pred_p,  
				\Post_p}
			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
		}%\]
\\
		\text{and~\qquad}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) 
 \\
\text{and\qquad }
 \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigotimes_{i=p-1}^{0}\Post_i} \\
 \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\
{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
		\land \!\!\bigwedge_{p=0}^n(\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i} = \beta_p\land \Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i} )
\\
\text{and~}
\Post=\Post\,' \uplus \bigotimes_{p=n}^0
		\Post_p  
		\end{mathpar} 
where $\Post_p$ only act upon variables of 
		$\Leaves(Q)$.
\end{lemma}

@@

And thus, because $\beta_{pj}^{j\in J\cap \Holes(Q)}$ are equal to the concatenation of  $(\beta'_{1pj})^{j\in J\cap \Holes(Q)}$, $(\beta'_{2j})^{j\in J\cap \Holes(Q)}$, and $(\beta_{3pj}')^{j\in J\cap \Holes(Q)}$ (re-indexed because we skipped some transitions), and additionally $(\beta_{1pj}')^{j\in J\cap \Holes(Q)}$, $(\beta_{2j}')^{j\in J\cap \Holes(Q)}$, and $(\beta_{3pj}')^{j\in J\cap \Holes(Q)}$ are identical to the hole labels $\beta_{1kj}^{j\in J\cap \Holes(Q)}$, $\beta_{2j}^{j\in J\cap \Holes(Q)}$, and $\beta_{3kj}^{j\in J\cap \Holes(Q)}$ (re-indexed) when $Q$ moves\footnote{more precisely, when $Q$ moves either $\beta_{1kj}^{j\in J\cap \Holes(Q)}$ is not empty  and thus $(\beta_{1pj}')^{j\in J\cap \Holes(Q)}=\beta_{1kj}^{j\in J\cap \Holes(Q)}$, or both are empty if the holes of $Q$ perform no action}. We can assert a similar equality on postconditions, i.e. between $\Post''_p$ and $\Post''_{1k}$, $\Post''_{2}$, $\Post''_{3k}$ where $\Post''_{1p}$ is the restriction of $\Post_{1p}$ over variables of $\Leaves(Q)$ (see initial decomposition, case 1, 2, and 3 above). Overall, we have
{\scriptsize \begin{equation*}
\begin{split}
\gamma_j^{j\in J\cap \Holes(Q)}&=\mybigdotcup_{i=0}^{m_1} \vis{\set{(\beta_{1i}')}\subst{\bigotimes_{j=i-1}^{0}\!\! \Post''_{1j}}}\dotcup  \vis{\set{\beta'_2}\subst{\bigotimes_{j=m_1}^{0}\Post''_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}} }\\
&=\mybigdotcup_{k=0}^n \left( \mybigdotcup_{i=n'_k}^{n'_{k+1}-1}\vis{\beta_{ij}^{j\in J\cap \Holes(Q)}\subst{\bigotimes_{j=i-1}^{n'_k}\!\!\Post''_{j}\bigotimes_{j=n'_k-1}^{0}\!\!\Post''_{j}}}\right)\\
&=\mybigdotcup_{k=0}^n \left( \gamma_{kj}^{j\in J\cap \Holes(Q)}\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{k}}\right)
\end{split}\end{equation*}
}
\[\forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i \text{see above}\]

\[ \Pred = \Pred\,'
		\land \!\!\bigwedge_{p=0}^n((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} )\]

@@

Finally we have:
\[\Post=\Post\,' \uplus \bigotimes_{p=n}^0
		\Post_p  \]

@@

\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose1} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
	Suppose $j_0\in J$  and additionally:\\[-2ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\beta_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
		\ostate{(s_i')^{\, i\in L}}}
}\\
\text{~~and~~}
Q\models{\openrule
	{
		\set{\gamma},
		 \Pred_Q,  
		\Post_Q}
	{\ostate{s_{i}^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
		\ostate{(s'_{i})^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Let 
\begin{mathpar}
%J_Q=\displaystyle{\bigcup_{t=0}^nJ_{t}}
%\qquad
\Pred\,'=\Pred\land (\beta_{j_0}=\alpha_Q\land \Pred_Q)
\\
%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
\Post\,'=\Post\uplus\Post_Q
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\set{\gamma}\uplus\vis{\beta_j^{j\in J\setminus \{j_0\}}}, 
			\Pred\,',  \Post\,'
			 }
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}
\begin{proof}
By  Lemma \ref{lem-rel-OT-WOT} we can decompose the WOT of $Q$ into  a series of $k+1$ and $k'+1$ tau open transitions and an observable open transition:

\[\forall h\!\in\![0..k].Q\models\openrule
    {\set{\beta_{1h}},\Pred_{1h},\Post_{1h}   }
         {\ostate{{(s_{1h})}} \OTarrow {\tau} \ostate{{(s_{1(h+1)})}}}
\]

\[Q\models{\openrule
	{
		\set{\beta_2},
		 \Pred_2,  
		\Post_2}
	{\ostate{s_{20}}\OTarrow {\alpha'_Q}
		\ostate{s_{21}}}
}
\]

\[
\forall h \in [0..k'].Q\models\openrule
         {
           \set{\beta_{3h}},\Pred_{3h}, \Post_{3h}}
         { \ostate{(s_{3h})} \OTarrow {\tau} \ostate{(s_{3(h+1)})}} \]

such that 
$\alpha_Q=\alpha'_Q\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$\\
$s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\

$\displaystyle{\set{\gamma}=\mybigdotcup_{h=0}^{k} \vis{\set{\beta_{1h}}} \dotcup  \vis{\set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}}}}
\\
\Pred_Q=\bigwedge_{h=0}^{k}\!\big(\Pred_{1h}\subst{\bigotimes_{j=h-1}^{0}\Post_j^1}\big)\land \Pred_2\subst{\bigotimes_{h=k}^{0}\Post_{1h}}\land\\~\qquad\qquad \bigwedge_{h=0}^{k'}\!\Pred_{3h}\subst{\bigotimes_{j=h-1}^{0}{\Post_{3j}}\otimes{\Post_2}  \otimes\bigotimes_{h=k}^{0}\Post_{1h}}
\\
\Post_Q=\bigotimes_{h=k'}^{0}\Post_{3h}\otimes\Post_2\otimes\bigotimes_{j=k}^{0}\Post_{1j}
$

@@

By Lemma \ref{lem-rel-OT-WOT} from cases $(1)$, $(2)$ and $(3)$ we obtain: 
\[P[Q]_{j_0}\!\models		
\openrule
    {
\set{\gamma'}, \Pred_c,
\Post_c}
         {\ostate{s_{10}\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha'} 
	\ostate{{{s'}^{i\in L}_{i}\uplus s_{3(k'+1)}}}}\] 
where
\[\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}} \]
and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$

\[\set{\gamma'}=\mybigdotcup_{h=0}^k\vis{\set{\beta_{1h}}} \dotcup \vis{{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'}\vis{\set{\beta_{3h}}}=\set{\gamma}\uplus\vis{\beta_j^{j\in J\setminus \{j_0\}}}\]
\[
\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_i{1i}}\land
\left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\\displaystyle
\bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigotimes_{i=h-1}^{0}{\Post_{3i}}\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}
\end{array}
\]

\[\Post_c=(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}
\]
Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\

>>>>

\begin{lemma}[Weak OT decomposition]\label{lem-decomposeWOT} 
	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
	lemma imply that $Q$ is 
	not a pLTS but a similar lemma can be proven for a pLTS $Q$}:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.  
		 Then there exist $n$, $\Pred\,'$,  
		$\Post\,'$,   and for all $p\in[0..n]$ there exist $\beta_p$, $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J_p\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
\text{\qquad and \qquad}\gamma_{j_0}=[\beta_0..\beta_n]
	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
		%\[
		Q\models{\openrule
			{
				\gamma_{p j}^{j\in J_p}, \Pred_p,  
				\Post_p}
			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
		}%\]
\\
		\text{such that~\qquad}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) 
\text{, }
 \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigotimes_{i=p-1}^{0}\Post_i}, \\
{~\hspace{2cm}}\Pred \iff \Pred\,'
		\land \!\!\bigwedge_{p=0}^n(\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i} = \beta_p\land \Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i} ),
\\
{~\hspace{2cm}}\Post=\Post\,' \uplus \bigotimes_{p=n}^0
		\Post_p,   \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\
		\end{mathpar} 
where $\Post_p$ only act upon variables of 
		$\Leaves(Q)$.
\end{lemma}

@@

And thus, because $\beta_{pj}^{j\in J\cap \Holes(Q)}$ are equal to the concatenation of  $(\beta'_{1pj})^{j\in J\cap \Holes(Q)}$, $(\beta'_{2j})^{j\in J\cap \Holes(Q)}$, and $(\beta_{3pj}')^{j\in J\cap \Holes(Q)}$ (re-indexed because we skipped some transitions), and additionally $(\beta_{1pj}')^{j\in J\cap \Holes(Q)}$, $(\beta_{2j}')^{j\in J\cap \Holes(Q)}$, and $(\beta_{3pj}')^{j\in J\cap \Holes(Q)}$ are identical to the hole labels $\beta_{1kj}^{j\in J\cap \Holes(Q)}$, $\beta_{2j}^{j\in J\cap \Holes(Q)}$, and $\beta_{3kj}^{j\in J\cap \Holes(Q)}$ (re-indexed) when $Q$ moves\footnote{more precisely, when $Q$ moves either $\beta_{1kj}^{j\in J\cap \Holes(Q)}$ is not empty  and thus $(\beta_{1pj}')^{j\in J\cap \Holes(Q)}=\beta_{1kj}^{j\in J\cap \Holes(Q)}$, or both are empty if the holes of $Q$ perform no action}. We can assert a similar equality on postconditions, i.e. between $\Post''_p$ and $\Post''_{1k}$, $\Post''_{2}$, $\Post''_{3k}$ where $\Post''_{1p}$ is the restriction of $\Post_{1p}$ over variables of $\Leaves(Q)$ (see initial decomposition, case 1, 2, and 3 above). Overall, we have
{\scriptsize \begin{equation*}
\begin{split}
\gamma_j^{j\in J\cap \Holes(Q)}&=\mybigdotcup_{i=0}^{m_1} \vis{\set{(\beta_{1i}')}\subst{\bigotimes_{j=i-1}^{0}\!\! \Post''_{1j}}}\dotcup  \vis{\set{\beta'_2}\subst{\bigotimes_{j=m_1}^{0}\Post''_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}} }\\
&=\mybigdotcup_{k=0}^n \left( \mybigdotcup_{i=n'_k}^{n'_{k+1}-1}\vis{\beta_{ij}^{j\in J\cap \Holes(Q)}\subst{\bigotimes_{j=i-1}^{n'_k}\!\!\Post''_{j}\bigotimes_{j=n'_k-1}^{0}\!\!\Post''_{j}}}\right)\\
&=\mybigdotcup_{k=0}^n \left( \gamma_{kj}^{j\in J\cap \Holes(Q)}\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{k}}\right)
\end{split}\end{equation*}
}
$\forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i$ (see above)\\
$\Pred = \displaystyle{\Pred\,'
		\land \!\!\bigwedge_{p=0}^n((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} )}$

@@

Finally we have:\\
$\Post=\displaystyle{\Post\,' \uplus \bigotimes_{p=n}^0
		\Post_p}$\\

@@

\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose1} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
	Suppose $j_0\in J$  and additionally:\\[-2ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\beta_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
		\ostate{(s_i')^{\, i\in L}}}
}
\quad\text{~~and~~}\quad
Q\models{\openrule
	{
		\set{\gamma},
		 \Pred_Q,  
		\Post_Q}
	{\ostate{s_{i}^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
		\ostate{(s'_{i})^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Let 
\begin{mathpar}
%J_Q=\displaystyle{\bigcup_{t=0}^nJ_{t}}
%\qquad
\Pred\,'=\Pred\land (\beta_{j_0}=\alpha_Q\land \Pred_Q) \quad\text{~~and~~}\quad
%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
\Post\,'=\Post\uplus\Post_Q
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\set{\gamma}\uplus\vis{\beta_j^{j\in J\setminus \{j_0\}}}, 
			\Pred\,',  \Post\,'
			 }
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}
\begin{proof}
By  Lemma \ref{lem-rel-OT-WOT} we can decompose the WOT of $Q$ into  a series of $k+1$ and $k'+1$ tau open transitions and an observable open transition:
\begin{mathpar}
\forall h\!\in\![0..k].Q\models\openrule
    {\set{\beta_{1h}},\Pred_{1h},\Post_{1h}   }
         {\ostate{{(s_{1h})}} \OTarrow {\tau} \ostate{{(s_{1(h+1)})}}}, \quad
Q\models{\openrule
	{
		\set{\beta_2},
		 \Pred_2,  
		\Post_2}
	{\ostate{s_{20}}\OTarrow {\alpha'_Q}
		\ostate{s_{21}}}
}, \\ \quad\text{~~and~~}\quad 
\forall h \in [0..k'].Q\models\openrule
         {
           \set{\beta_{3h}},\Pred_{3h}, \Post_{3h}}
         { \ostate{(s_{3h})} \OTarrow {\tau} \ostate{(s_{3(h+1)})}}
\end{mathpar}
such that\\ 
$\alpha_Q=\alpha'_Q\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$\\
$s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\
$\displaystyle{\set{\gamma}=\mybigdotcup_{h=0}^{k} \vis{\set{\beta_{1h}}} \dotcup  \vis{\set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}}}}
\\
\Pred_Q=\bigwedge_{h=0}^{k}\!\big(\Pred_{1h}\subst{\bigotimes_{j=h-1}^{0}\Post_j^1}\big)\land \Pred_2\subst{\bigotimes_{h=k}^{0}\Post_{1h}}\land\\~\qquad\qquad \bigwedge_{h=0}^{k'}\!\Pred_{3h}\subst{\bigotimes_{j=h-1}^{0}{\Post_{3j}}\otimes{\Post_2}  \otimes\bigotimes_{h=k}^{0}\Post_{1h}}
\\
\Post_Q=\bigotimes_{h=k'}^{0}\Post_{3h}\otimes\Post_2\otimes\bigotimes_{j=k}^{0}\Post_{1j}
$

@@

Using Lemma \ref{lem-rel-OT-WOT}, from cases $(1)$, $(2)$ and $(3)$ we get: 
\[P[Q]_{j_0}\!\models		
\openrule
    {
\set{\gamma'}, \Pred_c,
\Post_c}
         {\ostate{s_{10}\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha'} 
	\ostate{{{s'}^{i\in L}_{i}\uplus s_{3(k'+1)}}}}\] 
where\\
$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$
and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$.\\

$\set{\gamma'}=\mybigdotcup_{h=0}^k\vis{\set{\beta_{1h}}} \dotcup \vis{{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'}\vis{\set{\beta_{3h}}}=\set{\gamma}\uplus\vis{\beta_j^{j\in J\setminus \{j_0\}}}$\\
$\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_i{1i}}\land
\left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\\displaystyle
\bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigotimes_{i=h-1}^{0}{\Post_{3i}}\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}
\end{array}
$\\
$\Post_c=\displaystyle{(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}$

Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\
